Storage challenges in heterogeneous environments

### 2017-12-02 paper.tex
buidl stuff
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
title and authors
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
add motivations from malacology/declstore
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\documentclass{sig-alternate-05-2015}

@@

\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Noah Watkins, Michael Sevilla, Jeff LeFevre, Carlos Maltzahn
}

@@

>>>>

\documentclass{sig-alternate}

@@

\title{Storage challenges in heterogeneous environments}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Noah Watkins, Michael Sevilla, Jeff LeFevre, Carlos Maltzahn \\
\affaddr{University of California, Santa Cruz} \\
\affaddr{\{nmwatkin,msevilla,jlefevre,carlosm\}@ucsc.edu}
}

@@

The motivation for new storage interfaces is seeded in two widespread reactions
to heterogeneity: (1) developers are using non-standard interfaces, and (2)
developers spend a long time designing optimizations and system tunables.  For
(1), developers are already circumventing narrow interfaces to the storage
system using non-standard APIs to get the optimizations they
need~\cite{sevilla:es17-malac}.  Using these interfaces, application developers
push domain- and architecture-specific knowledge to the storage system, such as
how to logically access data stored on disk or which device type to store data
on, respectively.  This type of developer behavior is a direct response to
extreme heterogeneity.  For (2), developers are overwhelmed with the rapid
development and change associated with open-source storage
systems~\cite{watkins:hot17-declstor}. With so many active contributors,
software versions progress quickly and application optimizations that worked
for one version may not work for another; different hardware and configurations
make this permutation space practically impossible to reason about.

In light of new storage interfaces, we advocate the pursuit of the following
research directions.
